Highly Available Transactions: Virtues and Limitations

### 2013-04-01 writeup/evaluation.tex
foo

To better understand the impact of HAT versus non-HAT algorithms and
validate the latency-based analysis in Section~\ref{sec:latency}, we
deployed a basic distributed database prototype on public cloud
infrastructure. We compared the behavior of eventual consistency,
per-key mastering (wherein all operations required a RTT to a
designated master server), Read Committed, and TA with read your
writes guarantees. We deployed an experimental Java-based distributed
datastore backed by LevelDB both within and across EC2 regions and ran
the YCSB benchmark to determine the resulting performance impact. We
partitioned the database into two fully replicated clusters of three
\texttt{m1.xlarge} instances. For HAT, we stuck YCSB clients to their
local cluster and, to provide transactional functionality, grouped
every six YCSB operations from the default workload to form a
transaction. We report the median of five trials per experiment.

>>>>

To better understand the impact of HAT versus non-HAT algorithms and
validate the latency-based analysis in Section~\ref{sec:latency}, we
deployed a basic distributed database prototype on public cloud
infrastructure. We compared the behavior of eventual consistency,
per-key mastering (wherein all operations required a RTT to a
designated master server), Read Committed, and TA with read your
writes guarantees. We deployed an experimental Java-based distributed
datastore backed by LevelDB both within and across EC2 regions and ran
the YCSB benchmark~\cite{ycsb} to determine the impact of latency. We
partitioned the database into two fully replicated clusters of three
\texttt{m1.xlarge} instances. For HAT, we stuck YCSB clients to their
local cluster and, to provide transactional functionality, grouped
every six YCSB operations from the default workload to form a
transaction. We report the median of five trials per experiment.

### 2013-04-01 writeup/relatedwork.tex
foo

Weak consistency and high availability have been well
studied. Serializability has long been known to be
unachievable~\cite{davidson-survey} and Brewer's CAP Theorem has
attracted considerable attention~\cite{gilbert-cap}. The research has
begun to offer hints regarding the connection between ``weak
consistency'' and low latency~\cite{abadi-pacelc}, while several
studies examine weak isolation guarantees~\cite{adya,
  ansicritique}. However, as we have discussed, the connection between
weak consistency models in a distributed setting~\cite{calm, crdt} and
high availability is relatively unexplored. With the exception of a
preliminary workshop paper introducing HATs~\cite{hat-hotos}--- which
this work expands, providing impossibility results, a full
taxonomization, and experimental and application analysis (basically
all but Section 4.1)---we believe this paper is the first to explore
this area. Nonetheless, several studies rigorously classify non-HAT
semantics: Wisemann et al. have proposed a three parameter
classification for one-copy serializable database systems, performing
a more extensive classification than our overview in
Section~\ref{sec:evaluation}, including eager database replication
techniques~\cite{kemme-classification}. Additionally several earlier
surveys discuss distributed mechanisms for achieving one-copy
serializability~\cite{wisemann-survey}, linearizability, consistent
snapshots, and recency bounds~\cite{ceri-mechanism, chen-mechanism}.

>>>>

Weak consistency and high availability have been well
studied. Serializability has long been known to be
unachievable~\cite{davidson-survey} and Brewer's CAP Theorem has
attracted considerable attention~\cite{gilbert-cap}. The research has
begun to offer hints regarding the connection between ``weak
consistency'' and low latency~\cite{abadi-pacelc}, while several
studies examine weak isolation guarantees~\cite{adya,
  ansicritique}. However, as we have discussed, the connection between
weak consistency models in a distributed setting~\cite{calm, crdt} and
high availability is relatively unexplored. With the exception of a
preliminary workshop paper introducing HATs~\cite{hat-hotos}--- which
this work expands, providing impossibility results, a full
taxonomization, and experimental and application analysis (basically
all but Section 4.1)---we believe this paper is the first to explore
this area. Nonetheless, several studies rigorously classify non-HAT
semantics: Wisemann et al. have proposed a three parameter
classification for one-copy serializable database systems, performing
a more extensive classification than our overview in
Section~\ref{sec:evaluation}, including eager database replication
techniques~\cite{kemme-classification}. Additionally several earlier
surveys discuss distributed mechanisms for achieving one-copy
serializability~\cite{wisemann-survey}, linearizability, consistent
snapshots, and recency bounds~\cite{ceri-mechanism}.
